How residence time constrains diversity

### 2015-06-01 analyses/ResTime.Rmd
edited ResTime.Rmd to conduct many univariate examinations -KL

plot(t.tau, N, xlab="Particle Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau", col='SteelBlue')

plot(m.tau, N, xlab="Cell Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau", col='darkorchid4')

plot(t.tau, S, xlab="Particle Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau", col='SteelBlue')

plot(m.tau, S, xlab="Cell Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau", col='darkorchid4')

@@

N <- sim.data$TotalAbundance
plot(m.tau, log(N), xlab="Cell Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau",
     col='SteelBlue')

S <- sim.data$SpeciesRichness
plot(m.tau, log(S), xlab="Cell Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau",
     col='darkorchid4')

E <- sim.data$Evar
plot(m.tau, E, xlab="Cell Residence Time", 
     ylab="Species Evenness", 
     main = "Evenness vs. Tau",
     col='SteelBlue')

avg.ab <- N/S
plot(m.tau, log(avg.ab), xlab="Cell Residence Time", 
     ylab="Average Abundance",
     main = "N/S vs. Tau",
     col='darkorchid4')
```

@@

BP <- sim.data$BergerParker
plot(m.tau, BP, xlab="Cell Residence Time", 
     ylab="Berger-Parker", 
     main = "Relative Dominance",
     col='SteelBlue')

SimpD <- sim.data$InvSimpDiversity
plot(m.tau, SimpD, xlab="Cell Residence Time", 
     ylab="Simpsons, 1/D", 
     main = "Diversity",
     col='darkorchid4')

Skew <- sim.data$Skew
plot(m.tau, Skew, xlab="Cell Residence Time", 
     ylab="Skewness", 
     main = "Rarity",
     col='SteelBlue')

Nmax <- sim.data$Nmax
plot(m.tau, log(Nmax), xlab="Cell Residence Time", 
     ylab="Nmax",
     main = "Absolute Dominance",
     col='darkorchid4')
```

@@

plot(log(N), log(S), xlab="Total abundance",
     ylab="Species Richness", 
     main = "S vs. N",
     col='SteelBlue')

plot(log(N), log(Nmax), xlab="Total abundance", 
     ylab="Nmax", 
     main = "Nmax vs. N",
     col='darkorchid4')

plot(log(N), log(E), xlab="Total abundance", 
     ylab="Species Evenness", 
     main = "Evenness vs. N",
     col='SteelBlue')

plot(log(N), log(Skew), xlab="Total abundance", 
     ylab="Skewness",
     main = "Rarity vs. N",
     col='darkorchid4')
```

>>>>

plot(t.tau, N, xlab="Particle Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau", col='cornsilk4')

plot(m.tau, N, xlab="Cell Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau", col='cornsilk4')

plot(t.tau, S, xlab="Particle Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau", col='darkseagreen')

plot(m.tau, S, xlab="Cell Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau", col='darkseagreen')

@@

N <- sim.data$TotalAbundance
plot(m.tau, log(N), xlab="Cell Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau",
     col='cornsilk4')

S <- sim.data$SpeciesRichness
plot(m.tau, log(S), xlab="Cell Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau",
     col='darkseagreen')

E <- sim.data$Evar
plot(m.tau, E, xlab="Cell Residence Time", 
     ylab="Species Evenness", 
     main = "Evenness vs. Tau",
     col='skyblue')

avg.ab <- N/S
plot(m.tau, log(avg.ab), xlab="Cell Residence Time", 
     ylab="Average Abundance",
     main = "N/S vs. Tau",
     col='coral')
```

@@

BP <- sim.data$BergerParker
plot(m.tau, BP, xlab="Cell Residence Time", 
     ylab="Berger-Parker", 
     main = "Relative Dominance vs. Tau",
     col='firebrick')

SimpD <- sim.data$InvSimpDiversity
plot(m.tau, SimpD, xlab="Cell Residence Time", 
     ylab="Simpsons, 1/D", 
     main = "Diversity vs. Tau",
     col='gold')

Skew <- sim.data$Skew
plot(m.tau, Skew, xlab="Cell Residence Time", 
     ylab="Skewness", 
     main = "Rarity vs. Tau",
     col='limegreen')

Nmax <- sim.data$Nmax
plot(m.tau, log(Nmax), xlab="Cell Residence Time", 
     ylab="Nmax",
     main = "Absolute Dominance vs. Tau",
     col='sandybrown')
```

@@

plot(log(N), log(S), xlab="Total abundance",
     ylab="Species Richness", 
     main = "S vs. N",
     col='indianred')

plot(log(N), log(Nmax), xlab="Total abundance", 
     ylab="Nmax", 
     main = "Nmax vs. N",
     col='darkorange')

plot(log(N), E, xlab="Total abundance", 
     ylab="Species Evenness", 
     main = "Evenness vs. N",
     col='lightseagreen')

plot(log(N), Skew, xlab="Total abundance", 
     ylab="Skewness",
     main = "Rarity vs. N",
     col='plum')
```

growth <- sim.data$AvgPerCapita_GrowthRate
plot(m.tau, log(growth), xlab="Cell Residence Time", 
     ylab="growth", 
     main = "Per capita growth vs. Tau",
     col='dodgerblue')

maint <- sim.data$AvgPerCapita_Maintenance
plot(m.tau, SimpD, xlab="Cell Residence Time", 
     ylab="maintenance", 
     main = "Per capita maintenance vs. Tau",
     col='darkolivegreen')

immigration <- sim.data$Immigration_Rate
plot(m.tau, immigration, xlab="Cell Residence Time", 
     ylab="immigration", 
     main = "Immigration vs. Tau",
     col='mediumorchid')
```

res.conc <- sim.data$Resource_Concentration
plot(m.tau, log(res.conc), xlab="Cell Residence Time", 
     ylab="density", 
     main = "Resource density vs. Tau",
     col='peru')

res.div <- sim.data$Shannons_ResourceDiversity
plot(m.tau, res.div, xlab="Cell Residence Time", 
     ylab="Shannon's H", 
     main = "Resource diversity vs. Tau",
     col='palegreen')

res.rich <- sim.data$ResourceRichness
plot(m.tau, res.rich, xlab="Cell Residence Time", 
     ylab="Number of resource types", 
     main = "Resource richness vs. Tau",
     col='slateblue')
```
